%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : Tom치코 Vlach, Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Analysis of Mechanics%
}
\author{%
Tom치코 Vlach (xvlach24)%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} Hunt: Showdown

\item[] \textbf{Released:} 2019

\item[] \textbf{Author:} Crytek

\item[] \textbf{Primary Genre:} Extraction (First Person) Shooter

\item[] \textbf{Secondary Genre:} Survival Horror

\item[] \textbf{Style:} Stylized Realistic Western Look

\end{itemize}

}

\section*{\centering Analysis}

\subsection*{Overview}

Hunt showdown's primary gameplay mode and it's driving force is it's Bounty Hunt. In this game mode solos or teams from two to three players are put at edges of a medium sized open world heavily inspired and modeled after 1895 Louisiana swamp filled with sprawling compounds, cursed undead and nightmarish bosses hiding somewhere on the map. Players are then tasked with locating these bosses, killing them, banishing them and extracting with their bounties all while fighting hoards of undead and mainly other players trying to do the same thing as them.

The game also prides itself on highly accurate (even tho sometimes expanded) arsenal of late 19th century guns and weaponry including revolvers, hunting rifles and early semiautomatic weapons.

\subsection*{Multiple Genres}

The game was quite unique when it came out in 2019 with only other known extraction shooter being Escape from Tarkov (2017), which is much more realistic then Hunt but for casual players way too complicated to grab and go unlike Hunt. The game meshes several genres to accomplish it's blend of gameplay and they are first person shooter, survival horror, battle royal with other elements like team based gameplay and zombies which nowadays all combined is called extraction shooter (obviously without the zombies).

The combination of PvP and PvE (commonly just PvPvE) creates a perfect blend of action inside the game, where moments of high octane shootouts with other players is interspersed by tactical dispatching of the various AI zombies which means the game has little down time unless you actively choose to camp.

The game in my opinion also highly benefits from the pre-World War One weaponry as it slows down the gameplay and makes the shooting much more tactical in nature and less spraying and preying that you hit someone like most modern shooters that suffer from meta builds that can eliminate a player before they can even realize someone is attacking them.

\subsection*{Bosses and the Horrors of Bayout}

The game's realistic yet slightly stylized visual stile is perfect for all the various enemy designs ranging from classic zombies to the body horror of hives and mainly bosses of Bayout. All five of them are unique not only in their visual design but also gameplay one as every is countered differently and can kill inexperienced hunters within few seconds if not careful. With one exception all of them have some slight human characteristics or visual cues making it all the more horrifying when you realizes that the all of them were humans once, twisted by whatever is going on in the area.



\end{document}
